---
title: "Case Study"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(leaflet)
data("nyc_airbnb")

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)


theme_set(theme_minimal()+theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colur = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

## Load the dataset

```{r}
p8105.datasets::nyc_airbnb %>% 
  view

```

## Brainstorm some questions

Can use  slice to look at range of observations
Or sample_frac or sample_n to do the same 

* What is the relationship between price and rating. How about neighborhood and price. 
* what is the best Airbnb in staten island for <$100
* what price range is popular in each borough? Most rented?
* cheapest room type in each neighborhood?
* What apartment features are related to price
* Which hosts have higher ratings?

## Working through some of these questions

```{r}
nyc_airbnb %>% 
  janitor::clean_names() %>% 
  filter(neighbourhood_group == "Staten Island", price < 100) %>% 
  view
```

Data cleaning
```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2)
```

```{r}
nyc_airbnb %>% 
  count(neighbourhood_group, room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```


```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, room_type) %>% 
  summarize(mean_price = mean(price))
```

```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan") %>% 
  count(neighbourhood)

nyc_airbnb %>% 
  filter(
    price < 1000,
    neighbourhood_group == "Manhattan") %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price))+
  geom_boxplot()+
  coord_flip()
```

Coord flip flips x and y axis

```{r}
nyc_airbnb %>% 
  sample_n(1000) %>% 
  ggplot(aes(x = lat, y = long, color = price))+
  geom_point()
```

## Create a leaflet map

```{r}
pal <- colorNumeric("viridis", nyc_airbnb %>% pull(stars)) 

nyc_airbnb %>% 
  sample_n(5000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>%   addCircleMarkers(~lat, ~long, radius = 1, color =~ pal(stars))


```

